Minimizing post-shock forecasting error using disparate information

### 2020-07-27 manuscript/manuscript.tex
changes to introductions and revisions to Dave comments

In this article we provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock in real-time. Standard forecasting methods may not allow users to explore the consequences that structural shocks have on baseline forecasts \citep{baumeister2014real}. All is not lost in this setting, one may be able to supplement the present forecast with past data that contains similar structural shocks. The core idea of our methodology is to sensibly aggregate similar past realized shock-effects which arose from disparate time-series, and then incorporate the aggregated shock-effect estimator into the present forecast. Our method of combining disparate shock effects embraces ideas from conditional forecasting \citep{baumeister2014real, kilian2017structural}, time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, judgement forecasting \citep{svensson2005monetary, monti2008forecast}, synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, expectation shocks \citep{croushore2006data, clements2019measuring}.

@@

We now construct the aggregate estimators of the shock effects that appear in 
Forecast 2 (see Section \ref{forecast}). We use these to forecast response values $y_{1, T_1^*+1}$ assuming that $T_1^*$ is known.  %Notice that the shock effect 
%for time series $1$ is typically unobserved. But we can gather knowledge from 
%disparate time series to construct some sort of estimators that may be helpful for 
%estimating $\E{\alpha_1}$. 
First, we introduce the procedures of parameter estimation for 
$\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ (see Section \ref{modelsetup}). 
Conditional on all regression parameters, previous responses, and covariates, 
the response variable $y_{i,t}$ in $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ 
has distribution 
$$
  y_{i,t} 
    \sim N(\eta_i + \alpha_iD_{i,t} + \phi_i y_{i,t-1} + \theta_i'\x_{i,t} 
      + \beta_i'\x_{i,t-1}, \sigma^2).
$$
For $i = 2, \ldots, n$, all parameters in this model will be estimated with ordinary least squares 
(OLS) using historical data of $t = 1, \ldots, n_i$. For $i = 1$, we estimate all the parameters but $\alpha_1$ using OLS procedures for $t=1, \ldots, T_1^*$. In particular, let $\hat{\alpha}_i$, $i = 2, \ldots, n+1$ be the OLS estimate 
of $\alpha_i$.  Note that parameter estimation 
for $\mc{M}_1$ is identically the same as that for $\mc{M}_{21}$ or $\mc{M}_{22}$.

@@

@@

Our bootstrap procedures can be extended to approximate the distribution of shock effect estimators from more general time series. If the data are subject to heteroskedasticity of unknown form, bootstrapping tuples of regressands and regressors proposed by \citet{freedman1981bootstrapping} is robust in this situation with asymptotic validity in autoregressive models established by \citet{gonccalves2004bootstrapping}. If serial correlation exists in the data, various block bootstrapping procedures \citep{kunsch1989jackknife, liu1992moving} can be possible reasonable alternatives. Note that the pseudo time series generated by our proposed parametric bootstrap is not stationary. If stationarity is of concern, one can be referred to the stationary bootstrap invented \citet{politis1994stationary} for stationary and weakly dependent time series. Nevertheless, it was shown that approximation accuracy may be a cost for the stationary bootstrap in autoregressive  models in finite sample \citep{berkowitz1999finite}.  More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, \citet{berkowitz2000recent}, and Chapter 12 in \citet{kilian2017structural}. It is up to  users in terms of selecting which procedure to choose but under different assumptions on the time series.

>>>>

In this study, we investigate reliable forecasting for  time series that are to undergone a structural shock, which is not observed before, at a known time point. In this scenario, currently available forecasting methodologies are likely to fail since those  forecasts are trained on the data without any knowledge about the shock. It is a general problem that has many real-life implications for forecasting under unprecedented events. For example, an investor may be interested in forecasting the stock price of a company tomorrow after he  knew related news about an event that signals recessions today but he or she do not have available recent data for reliable prediction. Or, companies may be interested in forecasting the demand of their products to adjust production after they were involved in a brand crisis but they only have recent sales data for which the company is operating well. Nevertheless, it is still possible to do reliable forecasting by borrowing knowledge from similar disparate time-series in the sense that they experienced similar shocks in the past.

To formalize, we provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock in real-time. Standard forecasting methods may not allow users to explore the consequences that structural shocks have on baseline forecasts \citep{baumeister2014real}. All is not lost in this setting, one may be able to supplement the present forecast with past data that contains similar structural shocks. The core idea of our methodology is to sensibly aggregate similar past realized shock-effects which arose from disparate time-series, and then incorporate the aggregated shock-effect estimator into the present forecast. Our method of combining disparate shock effects embraces ideas from conditional forecasting \citep{baumeister2014real, kilian2017structural}, time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, judgement forecasting \citep{svensson2005monetary, monti2008forecast}, synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, expectation shocks \citep{croushore2006data, clements2019measuring}.

@@

We now construct the aggregate estimators of the shock effects that appear in 
Forecast 2 (see Section \ref{forecast}). We use these to forecast response values $y_{1, T_1^*+1}$ assuming that $T_1^*$ is known.  %Notice that the shock effect 
%for time series $1$ is typically unobserved. But we can gather knowledge from 
%disparate time series to construct some sort of estimators that may be helpful for 
%estimating $\E{\alpha_1}$. 
First, we introduce the procedures of parameter estimation for 
$\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ (see Section \ref{modelsetup}). 
Conditional on all regression parameters, previous responses, and covariates, 
the response variable $y_{i,t}$ in $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ 
has distribution 
$$
  y_{i,t} 
    \sim N(\eta_i + \alpha_iD_{i,t} + \phi_i y_{i,t-1} + \theta_i'\x_{i,t} 
      + \beta_i'\x_{i,t-1}, \sigma^2).
$$
For $i = 2, \ldots, n$, all parameters in this model will be estimated with ordinary least squares 
(OLS) using historical data of $t = 1, \ldots, n_i$. For $i = 1$, we estimate all the parameters but $\alpha_1$ using OLS procedures for $t=1, \ldots, T_1^*$. In particular, let $\hat{\alpha}_i$, $i = 2, \ldots, n+1$ be the OLS estimate 
of $\alpha_i$.  Note that parameter estimation 
for $\mc{M}_1$ is identically the same as that for $\mc{M}_{21}$ or $\mc{M}_{22}$.  We emphasize that $\alpha_i$s are random variables but the OLS estimation is conditioned on the their realizations from some distribution.

@@

\begin{remark}
  From Bayesian perspective, $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ can be interpreted as Bayes rules that minimize the posterior expected losses under different unknown loss functions.
\end{remark}

@@

Our bootstrap procedures can be extended to approximate the distribution of shock effect estimators from more general time series. If the data are subject to heteroskedasticity of unknown form, bootstrapping tuples of regressands and regressors proposed by \citet{freedman1981bootstrapping} is robust in this situation with asymptotic validity in autoregressive models established by \citet{gonccalves2004bootstrapping}. If serial correlation exists in the data, various block bootstrapping procedures \citep{kunsch1989jackknife, liu1992moving} can be possible reasonable alternatives. Note that the pseudo time series generated by our proposed parametric bootstrap are not stationary. If stationarity is of concern, one can be referred to the stationary bootstrap invented by \citet{politis1994stationary} for stationary and weakly dependent time series. Nevertheless, it was shown that approximation accuracy might be a cost for the stationary bootstrap in autoregressive  models in finite sample \citep{berkowitz1999finite}.  More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, \citet{berkowitz2000recent}, and Chapter 12 in \citet{kilian2017structural}. It is up to  users in terms of selecting which procedure to choose but under different assumptions on the time series.
